---
title: "Main title"
subtitle: "Sub title"
date: "`r format(Sys.Date(),  '%d %B %Y')`"
author:
  - name: Contact Name
    affiliation: Job title
    email: email@unhcr.org
output:
  unhcrdown::paged_simple:
    back_html: true
paged-footnotes: true
links-to-footnotes: true
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

```{css, echo=FALSE}
.col-ruler {
  column-rule: 2px solid #0072bc;
  column-gap: 30px;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment = "#>",
                      message=FALSE, 
                      warning=FALSE,
                      fig.width = 6.3,
                      fig.height = 4.4,
                      fig.retina = 2,
                      fig.align = "center",
                      fig.showtext = TRUE,
                      dev = "ragg_png",
                      dpi = 300)
```

**Column approach**

## Key figures

:::{.col2 .col-ruler}

<i class="fa-solid fa-person-walking-dashed-line-arrow-right blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Refugees

<i class="fa-solid fa-hands-holding-circle blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Asylum-seekers

<i class="fa-solid fa-person-rays blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Venezuelans displaced abroad

<i class="fa-solid fa-person-walking-arrow-right blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Internally displaced people

:::

<br>


```{r main_plot}
# Loading required packages
library(unhcrthemes)
library(tidyverse)
library(scales)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/comparison/column_stacked.csv")

# Plot
plot <- ggplot(df) +
  geom_col(aes(x = year,
               y = rst_in_thousand,
               fill = rst_type),
           width = 0.7) +
  geom_text(aes(x = year,
                y = rst_in_thousand,
                color = rst_type,
                label = rst_in_thousand),
            position = position_stack(vjust = 0.5),
            show.legend = FALSE,
            size = 8/.pt) +
  scale_color_manual(values = c("#000000", "#FFFFFF")) +
  scale_fill_unhcr_d(palette = "pal_unhcr",
                     nmax = 2,
                     order = 2:1) +
  scale_x_continuous(breaks = pretty_breaks(n = 11)) +
  scale_y_continuous(expand = expansion(c(0, 0.1))) +
  labs(title = "Resettlement by UNHCR and others | 2010-2020",
       subtitle = "Number of people (thousand)",
       caption = "Source: data source here\n© UNHCR, The UN Refugee Agency") +
  theme_unhcr(grid = FALSE,
              axis = "x",
              axis_title = FALSE,
              axis_text = "x")
plot
```

\newpage

**Float approach**

## Key figures

:::{.clearfix}

:::{.float-start}
<i class="fa-solid fa-person-walking-dashed-line-arrow-right blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Refugees

<i class="fa-solid fa-hands-holding-circle blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Asylum-seekers
:::

:::{.float-end}
<i class="fa-solid fa-person-rays blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Venezuelans displaced abroad

<i class="fa-solid fa-person-walking-arrow-right blue" style="font-size: 2em;"></i><br>**[XXX,XXX]{.blue .lead}** Internally displaced people
:::

:::

<br>


```{r plot2}
plot
```