---
title: "Main presentation title"
subtitle: "Subtitle if needed"
author: "Your name"
institute: "Bureau/Divisions"
date: "`r format(Sys.Date(),  '%d %B %Y')`"
output:
  unhcrdown::html_slides:
      nature:
        highlightStyle: github
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# HTML presentation

.bg-blue[
C'est la vie `mon super code` j'ai vraiment .blue[beaucoup de chance] kfsajsadf kjsafhjkse aeoifhjeo soaifhoiswae awsfioefoia faoiwesfhjoiewf weoifjaweof eskwfjaowief aweoifjawoeifj foiawejf
]
.pull-left[
```{r, eval=FALSE, fig.height=5}
data(idp, package = "unhcrthemes")
idp_total <- idp |>
  group_by(year) |>
  summarise(idp = sum(idp, na.rm = TRUE) / 1e6) |>
  ungroup()
ggplot(idp_total) +
  geom_col(aes(x = year, y = idp),
           fill = unhcr_pal(n = 1, "pal_blue"),
           width = 0.8) +
  labs(title = "Globalement IDP displacement | 2010 - 2020",
       y = "Number of people (in million)",
       caption = "Source: UNHCR Refugee Data Finder\n© UNHCR, The UN Refugee Agency") +
  scale_y_continuous(expand = expansion(c(0, 0.1))) +
  scale_x_continuous(breaks = scales::pretty_breaks(10)) +
  theme_unhcr(grid = "Y", axis_title = "y")
```
]

.pull-right[
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
glimpse(iris)
```
]

.footnote[
[1] https://github.com/yihui/xaringan

[2] https://slides.yihui.org/xaringan/
]


---
class: center, middle

# Section title

### An interesting new Section

---

# Basic style

The templates comes with .bg-blue[predefined] styles for inline text, such as *italic*, **bold** or <u>underline text</u>.

It also includes the requires styles for common elements such as:

.pull-left[
**Headers:**

## Heading 2

### Heading 3

**Lists:**

* item 1
* item 2
    1. sub-item 2.1
    2. sub-item 2.2
]

.pull-right[

**Or quotes:**

> It is further proof that refugee movements and the broader issue of migration of populations ... is a global challenge that cannot be confined to a few countries.
>
> Filippo Grandi

]

---
class: inverse, center, middle

# Section title - Dark

### An interesting new Section

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---
background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
class: bottom, inverse, hide-logo

### Or a full page picture with no logo

---

# Reveal

Here's a new slide that show piece by piece

--

* One

--

* Two

--

* Three

---
class: inverse, center, middle

# Thank you

### Goodbye slide
